The Effects of Neighborhood Income and Race In Moderating the Effect of Heat on Expressed Mood in the United States

### 2022-02-16 doc/author-response-to-reviewers.tex

- Note that EHP is required by law to conform to 508 standards for accessibility, which provides guidelines to ensure that the content is accessible in some form to all readers, including those with color vision disabilities. In general, do not identify elements of a figure by color alone, as individuals with color vision disabilities will not be able to discern that color. Instead, use contrast, texture, or symbols. Color may be used to enhance figures, but to ensure that figures are accessible to readers with impaired color vision, color should not be used as the only means of conveying information unless absolutely necessary. Use different symbols, shading/textures, and line patterns instead of (or in addition to) color to distinguish among different data points, or use contrasting colors that can be easily distinguished from each other when the figure is printed in black and white. Alternatively, select a “colorblind palette” if available in the software package being used to generate the figure. If colors are used to identify data, include a color key in the graphical portion of the figure: do not refer to colors by name (i.e., red, blue) in the figure title or caption. For example: Figure 2.
- Revise figure captions: Tables and figures do not have to be 100\% stand-alone, but they should include enough information to be easily interpreted by a casual reader who may be “skimming” the manuscript to decide whether it is worth a more detailed assessment. This applies to tables and figures provided in the separate Supplemental Material file, as well as tables and figures in the main text. If you are in doubt about the amount of information to include, please err on the side of excess information.
o Provide brief information about the study population (including location, overall size, and time period), usually in the table or figure title.
o Tables or figures reporting model-based estimates should include brief information regarding the methods used to derive the estimates, including the type of model, covariates, missing data methods (e.g., imputation), and methods to account for values o Report numbers of observations used to derive each individual estimate reported in the table or figure, after accounting for missing data and subgrouping. As appropriate, indicate numbers of observations by subgroup. (These can be provided in the supplemental material)
